Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-14 MS/ms.Rmd
Added survey results relevant to questioons, plus a figure.

pacman::p_load(dplyr,ggplot2,here, pander, janitor)

@@

hetero <- dat %>%  janitor::tabyl(cont_moderator_variable)
hetero_dealt <- dat %>%  filter(!cont_moderator_variable_modelled=="") %>% janitor::tabyl(cont_moderator_variable_modelled)
weighted <- dat %>% janitor::tabyl(meta_analysis_weighted) 
weighted_meta <- dat %>% filter(meta_analysis_self_described == "yes") %>% janitor::tabyl(meta_analysis_weighted) 
```

Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively - See *Supplementary Materials* for a full breakdown). In many cases, studies make use of multiple effect size measures. Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance hetreogenity' in some form or another, and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it; usually through meta-regression modelling. Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean.

```{r, fig1, fig.cap="test"}
p1 = 
p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = cont_moderator_variable,
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  labs(x = "Nuisance Heterogenity?",
       y = "Proportion",
       fill = "Modelled Nuisance\n Heterogenity?")

@@

@@

tablea

>>>>

pacman::p_load(dplyr,ggplot2,here, pander, janitor, patchwork)

@@

hetero <- dat %>%  janitor::tabyl(cont_moderator_variable)
hetero_dealt <- dat %>%  filter(!cont_moderator_variable_modelled=="") %>% janitor::tabyl(cont_moderator_variable_modelled)
weighted <- dat %>% janitor::tabyl(meta_analysis_weighted) 
weighted_meta <- dat %>% filter(meta_analysis_self_described == "yes") %>% janitor::tabyl(meta_analysis_weighted)

summary <-  dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
  dplyr::summarise(`Multilevel Meta-analysis Model` = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
                  `Multilevel Metaregression Model` = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
                    `Linear Regression` = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
                 `Vote Counting` = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
                 `Weighted Regression` = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
                 `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(effect)
rownames(summary) <- NULL

het_reported <- dat %>%  filter(!heterogeneity_reported=="N/A (e.g. they conducted unweighted meta-analysis)") %>% mutate(heterogeneity_reported = if_else(heterogeneity_reported == "unclear/other (add comment)", "other", heterogeneity_reported)) %>% janitor::tabyl(heterogeneity_reported)
```

Quantitative syntheses in comparative physiology commonly analyse raw summary statistics (`r with(effects, effects[effect == "Means","prop"])*100`\% of studies), followed closely by Fishers transformed correlation coefficients (Zr) (`r with(effects, effects[effect == "Zr","prop"])*100`\% of studies), standardised mean differences (SMD) and log response ratios (lnRR) (`r with(effects, effects[effect == "SMD","prop"])*100`\% and `r with(effects, effects[effect == "lnRR","prop"])*100`\%, respectively; Figure \@ref(fig:fig1)A). In many cases, studies make use of multiple effect size measures. Approximately `r with(hetero, hetero[cont_moderator_variable == "yes","percent"])*100`\% of effect sizes used within the study were deemed to be impacted by 'nuisance heterogeneity' in some form or another (Figure \@ref(fig:fig1)B), and of the studies where this was the case, only `r with(hetero_dealt, hetero_dealt[cont_moderator_variable_modelled == "yes","percent"])*100`\% of the studies clearly dealt with it (Figure \@ref(fig:fig1)B); usually through meta-regression modelling. Overall, `r with(weighted, weighted[meta_analysis_weighted == "weighted model","percent"])*100`\% of studies used a weighted meta-analytic model, however, of the studies self described as 'meta-analyses', `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","percent"])*100`\% (N = `r with(weighted_meta, weighted_meta[meta_analysis_weighted == "unweighted model","n"])` of `r with(weighted_meta, sum(weighted_meta[,"n"]))`) did not actually weight their meta-analytic mean. Many studies used 'Linear Regression' (including linear and generalised linear mixed effects models) as the main type of model fit to the data (Figure \@ref(fig:fig1)C). Of the studies using weighted meta-analytic models `r with(het_reported, sum(het_reported[1:2,"percent"])*100)`\% (N = `r with(het_reported, sum(het_reported[1:2,"n"]))` meta-analyses) did not report any measure of heterogeneity.

```{r, fig1, fig.cap="**Summary of meta-analytic practices in comparative physiology.** (A) Different types of effect measures commonly used in meta-analyses and their releative frequency of use. (B) how many meta-analyses where 'nuisance heterogenity' have the potential to impact effect sizes, and the proportion of studies explicitly dealing with nuisance heterogenity. (C) Frequency of analytical approaches used to analyse effect measures. Note that only 'Weighted Regression', 'Random Effects Models', 'Multilevel Metaregression Models' and 'Multilevel Meta-analysis Models' are weighted models."}
p1 = dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  ggplot() + tm + 
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,0.35)) +
  labs(x = "Effect Size",
       y = "Frequency") +
  coord_flip()

p2 = dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = cont_moderator_variable,
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  theme(legend.position = c(0.50, 0.8)) + 
  labs(x = "Nuisance Heterogeneity?",
       y = "Frequency",
       fill = "Modeled Nuisance\nHeterogeneity?") 
p3 <- summary %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  labs(x = "Analytical Approach",
       y = "Frequency") +
  coord_flip()

p1 + p2 + p3 + plot_annotation(tag_levels = c("A"), tag_prefix = "(", tag_suffix = ")")

@@

FitFlextableToPage <- function(ft, pgwidth = 6){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

@@

FitFlextableToPage(tablea, pgwidth = 8)
